Paper changepoint

### 2019-01-08 paper-comparison/paper_changepoint.Rmd
Report mean cpt estimates for paper changepoint

>>>>

# find means on each changepoint:
mean(df_4[df_4$variable=='V1','value']) %>% date_decimal() %>% format('%d-%m-%Y')
mean(df_4[df_4$variable=='V2','value']) %>% date_decimal() %>% format('%d-%m-%Y')
mean(df_4[df_4$variable=='V3','value']) %>% date_decimal() %>% format('%d-%m-%Y')
mean(df_4[df_4$variable=='V4','value']) %>% date_decimal() %>% format('%d-%m-%Y')
